Rank Recovery

### 2020-11-18 output_scripts/rank_recovery.Rmd
correct typo in glicko ranks and begin creating plot for this
small change to compare more methods

all_sims <- list()
for(i in seq_along(sim_files)) {
 single_fit <- readRDS(here("output", "rank_sims", 
                            "sims_m3_dc_isi",
                            sim_files[i]))
 all_sims[[i]] <- single_fit
}

spear <- function(sim_data) {
  truth <- sim_data$truth
  sim_data %>%
    select(m1:isi) %>%
    map( ~cor.test(truth, .x,
                   method = "spearman")$estimate  ) %>%
    enframe() %>%
    unnest(cols = c(value))
}

@@

sim_data$name <- case_when(
          name == "isi" ~ "I&SI",
          name == "m1" ~ "C-HP",
          name == "m2" ~ "C-DCHP",
          name == "m3_dc" ~ "C-MMHP")

sim_data$name <- factor(sim_data$name, levels = c("I&SI","C-HP",
                                                  "C-DCHP", "C-MMHP"))

@@

gl_ranks <- rev(gl_train$ratings$Player)
# highest to lowest

>>>>

all_sims <- list()
for(i in seq_along(sim_files)) {
 single_fit <- readRDS(here("output", "rank_sims", 
                            "sims_m3_dc_isi_sparse",
                            sim_files[i]))
 all_sims[[i]] <- single_fit
}

spear <- function(sim_data) {
  truth <- sim_data$truth
  sim_data %>%
    select(m1:glicko) %>%
    map( ~cor.test(truth, .x,
                   method = "spearman")$estimate  ) %>%
    enframe() %>%
    unnest(cols = c(value))
}

@@

sim_data$name <- case_when(
          name == "isi" ~ "I&SI",
          name == "m1" ~ "C-HP",
          name == "m2" ~ "C-DCHP",
          name == "m3_dc" ~ "C-MMHP",
          name == "agg" ~ "AggRank",
          name == "glicko" ~ "Glicko")

sim_data$name <- factor(sim_data$name, levels = c("I&SI",
                                                  "AggRank",
                                                  "Glicko",
                                                  "C-HP",
                                                  "C-DCHP",
                                                  "C-MMHP"))

@@

gl_ranks <- rev(gl_train$ratings$Rating)
# highest to lowest
